\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the POC demo and the Rev
0 demo.

\section{Demo Plans}

\begin{itemize}
    \item Demonstrate working client program front-end: the user shall be able to input a plain-text title of a song, receive Spotify preview options, select the desired song from amongst them, then be displayed a collection of Spotify preview songs as recommendation output. \textcolor{red}{May also demonstrate audio file input}.
    \item \emph{Optionally}, show database schema and a sample of database query results.
    \item \emph{Optionally}, briefly explain how a subset of the features are extracted, and potentially relevant visualizations. A full list of features follows:
    \begin{itemize}
        \item Dynamic Range.
        \item Tempo (Beats Per Minute).
        \item Frequency Range.
        \item Root Mean Square (Average Loudness).
        \item Key \& Scale.
        \item Timbre.
        \item Vocal Gender.
        \item Instrumentalness.
        \item \emph{Latent (derived) features}.
        \item \emph{Contour (as a derived feature)}.
    \end{itemize}
\end{itemize}

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 26\\
Ansel Chen & 23\\
Muhammad Jawad & 19\\
Mohamad-Hassan Bahsoun & 23\\
Matthew Baleanu & 24\\
Ahmed Al-Hayali & 26\\
\bottomrule
\end{tabular}
\end{table}

\emph{No meetings were missed by any of the team members since the POC team contribution report. The only meeting that may appear so was between Ansel \& Ahmed just before the POC alignment meeting, which was not necessary.}

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 1\\
Ansel Chen & 1\\
Muhammad Jawad & 1\\
Mohamad-Hassan Bahsoun & 1\\
Matthew Baleanu & 1\\
Ahmed Al-Hayali & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 13\\
Ansel Chen & 11\\
Muhammad Jawad & 10\\
Mohamed-Hassan Bahsoun & 12\\
Matthew Baleanu & 10\\
Ahmed Al-Hayali & 12\\
\bottomrule
\end{tabular}
\end{table}

\emph{No lectures were missed by any of the team members since the POC team contribution report.}

\section{TA Document Discussion Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 4\\
Ansel Chen & 4\\
Muhammad Jawad & 4\\
Mohamed-Hassan Bahsoun & 4\\
Matthew Baleanu & 4\\
Ahmed Al-Hayali & 4\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 349 & 100\% \\
Ansel Chen & 64 & 18.34\% \\
Muhammad Jawad & 76 & 21.78\% \\
Mohamed-Hassan Bahsoun & 46 & 13.18\% \\
Matthew Baleanu & 62 & 17.77\% \\
Ahmed Al-Hayali & 101 & 28.94\% \\
\bottomrule
\end{tabular}
\end{table}

The commits-to-main were tracked using GitHub's \href{https://github.com/AhmedAl-Hayali/GenreGuru/graphs/contributors}{Insights}. Multi-author commits were used where appropriate, so commits are representative of contribution.

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Ansel Chen & \href{https://github.com/AhmedAl-Hayali/GenreGuru/issues?q=is%3Aissue+author%3Achenans1+}{4+9} & \href{https://github.com/AhmedAl-Hayali/GenreGuru/issues?q=is%3Aissue+is%3Aclosed+assignee%3Achenans1+}{68} \\
Muhammad Jawad & \href{https://github.com/AhmedAl-Hayali/GenreGuru/issues?q=is%3Aissue+author%3Ajawadsalwati}{5+37} & \href{https://github.com/AhmedAl-Hayali/GenreGuru/issues?q=is%3Aissue+is%3Aclosed+assignee%3Ajawadsalwati}{62} \\
Mohamed-Hassan Bahsoun & \href{https://github.com/AhmedAl-Hayali/GenreGuru/issues?q=is%3Aissue+author%3Abahsounm+}{1+26} & \href{https://github.com/AhmedAl-Hayali/GenreGuru/issues?q=is%3Aissue+is%3Aclosed+assignee%3Abahsounm+}{88} \\
Matthew Baleanu & \href{https://github.com/AhmedAl-Hayali/GenreGuru/issues?q=is%3Aissue+author%3Abaleanum}{2+31} & \href{https://github.com/AhmedAl-Hayali/GenreGuru/issues?q=is%3Aissue+is%3Aclosed+assignee%3Abaleanum}{73} \\
Ahmed Al-Hayali & \href{https://github.com/AhmedAl-Hayali/GenreGuru/issues?q=is%3Aissue+author%3AAhmedAl-Hayali+}{51+77} & \href{https://github.com/AhmedAl-Hayali/GenreGuru/issues?q=is%3Aissue+is%3Aclosed+assignee%3AAhmedAl-Hayali+}{79} \\
\bottomrule
\end{tabular}
\end{table}

All numbers were found using GitHub Issues' \href{https://docs.github.com/en/search-github/searching-on-github/searching-issues-and-pull-requests}{advanced search syntax}, and each meric is hyperlinked to the corresponding query.

\section{CICD}

No CI/CD infrastructure has been set up yet.

\end{document}